---
title: "twitter-shiny"
author: "Caleb Trujillo"
date: "1/24/2021"
output: html_document
runtime: shiny
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
pacman::p_load(rtweet,syuzhet, tidyverse, DT, stringr, wordcloud, tidytext)
#remotes::install_github("ropensci/rtweet")
#library(rtweet)
#auth_setup_default()
```

This R Markdown document is made interactive using Shiny. 


```{r load data, eval = FALSE, include=FALSE, skip = TRUE}
tweets <- search_tweets(q = "#rstats", 
                        n = 16000,
                        include_rts = FALSE,
                        `-filter` = "replies")
         
                        
user_timeline  <- get_timeline("RLadiesSeattle", n = 900)

```

```{r load Rdata, eval = TRUE, include=FALSE}
load("~/workspace/Twitter-shiny/data.RData")
```
## Twitter data {.tabset}

### Recent Rstats tweets

The plot below shows time series of #rstats tweets and can be filtered by language.

```{r tweets, echo=FALSE}
inputPanel(
  selectInput("tweetlang", label = "Language of tweets:",
              choices = unique(tweets$lang), selected = "en", multiple = TRUE)
)


renderPlot({
  ts_plot(tweets %>% filter(lang %in% input$tweetlang) , by = "hours", col = "blue")  +
    labs(x = NULL, y = NULL,
       title = "Frequency of tweets from containing #Rstats",
       subtitle = paste0(format(min(tweets$created_at), "%d %B %Y"), " to ", format(max(tweets$created_at),"%d %B %Y")),
       caption = "Data collected from Twitter's REST API via rtweet") + 
    theme_minimal()
})

renderDataTable({
  tweets %>% 
    filter(lang %in% input$tweetlang) %>% 
    select(screen_name,text,lang,favorite_count,retweet_count)
})
```


### Tweets from @RLadiesSeattle

The plots below show the top emojis used, a wordle of terms, and a time series of tweets by @RLadiesSeattle. The time series can be plotted with different sources to see when different devices were used to tweet.

#### Time series plot of tweets

```{r user, echo=FALSE}
inputPanel(
  selectInput("tweetsource", label = "Source of tweets:",
              choices = unique(user_timeline$source), selected = unique(user_timeline$source), multiple = TRUE)
)

renderPlot({
  ts_plot(user_timeline %>% filter(source %in% input$tweetsource), by = "months", col = "blue") +
    labs(x = NULL, y = NULL,
       title = "Frequency of tweets from @RLadiesSeattle",
       subtitle = paste0(format(min(tweets$created_at), "%d %B %Y"), " to ", format(max(tweets$created_at),"%d %B %Y")),
       caption = "Data collected from Twitter's REST API via rtweet") + 
    theme_minimal()
})

renderDataTable({
  user_timeline %>% 
    filter(source %in% input$tweetsource) %>% 
    select(text, favorite_count, retweet_count, source) %>%
    arrange(desc(retweet_count))
})

```

#### Top emojis

```{r emoji, echo=FALSE}
renderTable({
  user_timeline %>%
  mutate(emoji = ji_extract_all(text)) %>%
  filter(source %in% input$tweetsource) %>%
  unnest(cols = c(emoji)) %>%
  count(emoji, sort = TRUE) %>%
  top_n(10)
})
```

#### Wordle: A graphic of frequently used words.

```{r userwordle , echo=FALSE}
renderPlot({
 words <- user_timeline %>%
  mutate(text = str_remove_all(text, "&amp;|&lt;|&gt;"),
         text = str_remove_all(text, "\\s?(f|ht)(tp)(s?)(://)([^\\.]*)[\\.|/](\\S*)"),
         text = str_remove_all(text, "[^\x01-\x7F]")) %>% 
  unnest_tokens(word, text, token = "tweets") %>%
  filter(!word %in% stop_words$word,
         !word %in% str_remove_all(stop_words$word, "'"),
         str_detect(word, "[a-z]"),
         !str_detect(word, "^#"),         
         !str_detect(word, "@\\S+")) %>%
  filter(source %in% input$tweetsource) %>%
  count(word, sort = TRUE)

words %>% 
  with(wordcloud(word, n, random.order = FALSE, max.words = 100, colors = "#F29545")) 
})
```
